Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-22 latex/article.tex
upgrade figure 5
Added part of the figures on the paper

\begin{table}
  \begin{center}
    \begin{tabular}{@{}lrrrrrrrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=$}   & \multicolumn{6}{c}{$R=$}\\
      \cmidrule(r){2-12}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches & & & & & & & & & & & &\\
      Time (in ms) & & & & & && & & & & &\\
      $L_\infty$ error (\wrt $l_0$) & & & & & && & & & & &\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

@@

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
	  bar width=15pt,
	  nodes near coords,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.20)},
            anchor=north,legend columns=-1},
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2,
	    xxx-R1, xxx-R2},
          xtick=data,
          x tick label style={rotate=45,anchor=east},
        ]
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2)
          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0)
          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2)
          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
    \end{tikzpicture}
     \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
	  bar width=15pt,
	  nodes near coords,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.20)},
            anchor=north,legend columns=-1},
         % ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2,
	    xxx-R1, xxx-R2},
          xtick=data,
          x tick label style={rotate=45,anchor=east},
        ]
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2)
          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0)
          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2)
          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
       % \legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
    \end{tikzpicture}
  \end{center}
  \caption{Adaptive timings H vs. rafined (tout : adaptatif, 2 rayons par formes, 4
    formes + images).}
  \label{fig:timings}
\end{figure}

>>>>

\begin{table}
  \begin{center}
%    \begin{tabular}{@{}lrrrrrrrrrrr@{}}
%      \toprule
%      & \multicolumn{5}{c}{$R=8$}   & \multicolumn{6}{c}{$R=16$}\\
%      \cmidrule(r){2-12}
%    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
%      \midrule
%      Number of texture fetches &
%      1468 & 2 & 28 & 260 & 2104 & 
%      5706 & 2 & 28 & 90 & 2120 & 1780\\
%      Time (in ms) &
%      208 & 15 & 26 & 93 & 642 &
%      826 & 14 & 26 & 252 & 606 & 4801\\
%      $L_\infty$ error (\wrt $l_0$) &
%      0.051 & 0.306 & 0.085 & 0.047 & 0 & 
%      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
%      $L_2$ error (\wrt $l_0$) &
%      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0 & 
%      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
%      \bottomrule
%    \end{tabular}

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      Time (in ms) &
      208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 1780\\
      Time (in ms) &
      826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}

  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

@@

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2, 
	      xxx-R1, xxx-R2},
          xtick=data,
          point meta=rawy,	
          x tick label style={rotate=45,anchor=east},
        ]
        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000) 
          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000) 
          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000) 
          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000) 
          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}

     \end{tikzpicture}
     \end{center}
  \caption{Adaptive timings H vs. rafined (tout : adaptatif, 2 rayons par formes, 4
    formes + images).}
  \label{fig:timings}
\end{figure}
